The Strucplot Framework:\\ Visualizing Multi-way Contingency Tables with \pkg{vcd}

### 2006-09-15 trunk/vcd/paper/Strucplot/JSS.Rnw
-new argument for color of unshaded zeros -panel-functions of cotabplot compute prefix on their own.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@567 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{table}[h]
  \centering
  \begin{tabular}{|l|c|c|c|c|c|}
    \hline
                             & \proglang{SAS} & \proglang{S-PLUS} & \proglang{R} & \pkg{ViSta} & \pkg{MANET}/\pkg{Mondrian}\\\hline
    Basic functionality      &  $\times$  &   $\times$    & $\times$ &   $\times$   & $\times$\\
    Shape                    &     &        & $\times$ &       & $\times$\\
    Residual-based shadings  &  $\times$  &        & $\times$ &   $\times$   & ($\times$)\\
    Conditional Views        &  $\times$  &        & $\times$ &       & $\times$\\
    Interaction              &     &        &   &   $\times$   & $\times$\\
    Extensible Design        &     &        & $\times$ &       &  \\\hline
  \end{tabular}
  \caption{Comparison of current software environments.}
  \label{tab:compare}
\end{table}

>>>>

\begin{table}[h]
  \centering
  \begin{tabular}{|l|c|c|c|c|c|}
    \hline
                             & \proglang{SAS} & \proglang{S-PLUS} &
                             \proglang{R} & \pkg{ViSta} & \pkg{MANET}
                             & \pkg{Mondrian}\\\hline
    Basic functionality      &  $\times$  &   $\times$    & $\times$ &   $\times$   & $\times$& $\times$\\
    Shape                    &     &        & $\times$ & $\times$  & &\\
    Residual-based shadings  &  $\times$  &        & $\times$ &   highlighting   &($\times$)& ($\times$)\\
    Conditional Views        &  $\times$  &        & $\times$ & $\times$ & &\\
    Interaction              &     &        &   &   $\times$   & $\times$& $\times$\\
    Linking                  &     &        &   &              & $\times$& $\times$\\
    Extensible Design        &     &        & $\times$ &       &  &\\
    Language                 & SAS & S & S & XLisp & ?? & Java\\
\hline
  \end{tabular}
  \caption{Comparison of current software environments.}
  \label{tab:compare}
\end{table}
